---
title: "10-import"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

# Data description 

The medv variable is the target variable.

The Boston data frame has 506 rows and 14 columns.

This data frame contains the following columns:

crim

per capita crime rate by town.

zn

proportion of residential land zoned for lots over 25,000 sq.ft.

indus

proportion of non-retail business acres per town.

chas

Charles River dummy variable (= 1 if tract bounds river; 0 otherwise).

nox

nitrogen oxides concentration (parts per 10 million).

rm

average number of rooms per dwelling.

age

proportion of owner-occupied units built prior to 1940.

dis

weighted mean of distances to five Boston employment centres.

rad

index of accessibility to radial highways.

tax

full-value property-tax rate per $10,000.

ptratio

pupil-teacher ratio by town.

black

1000(Bk - 0.63)^2 where Bk is the proportion of blacks by town.

lstat

lower status of the population (percent).

medv

median value of owner-occupied homes in $1000s.

## loading pkgs
```{r pkgs, message=FALSE}
library(tidyverse)
library(ggplot2)
library(fs)
library(purrr)
library(stringr)
library(assertr)
library(caret)
library(janitor)
```

## load data

```{r load data, message=FALSE}
df <- read_csv("./data/BostonHousing.csv") %>% clean_names()
```

## some functions
```{r functions}
#for check how many unique values for each variable.
col_uni <- function(df){
  map(
    map(df,unique), # apply the unique function to each column, return the unique value of each column.
    length) #apply the length function to the unique value of each column, return how long the unique value is for each column so that we can know how many unique values for each column.
}
```


## overview

```{r #dataoverview}
str(df)
```
## check the dataset
```{r check}
# check how many missing values in our dataset, result is 0.
sum(is.na(df))

# check the limit (based on description) for each variable 
df %>% 
  assert(in_set(c(1, 0)), chas)%>% 
  assert(in_set(c(0:24)), rad)%>% 
  assert(within_bounds(0,1), nox) %>%
  assert(within_bounds(0,100), zn)%>%
  assert(within_bounds(0,100), crim)%>%
  assert(within_bounds(0,Inf),indus)%>%
  assert(within_bounds(0,120), age) %>%
  assert(within_bounds(0,Inf), dis) %>%
  assert(within_bounds(0,100), ptratio) %>%
  assert(within_bounds(0,Inf), tax) %>%
  assert(within_bounds(0,Inf), medv) %>%
  assert(within_bounds(0,Inf), b) %>%
  assert(within_bounds(0,100), lstat)
```

## check how many unique values each variables have.

From the result below, we can find that there are some variables only have few unique values.

Combining the result below with the information from the data description,"rad" & "chas" should be factor variables.
```{r check var}
col_uni(df)
```
