---
title: "10-import"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
# Describe the data and the problem

I am interested in what will affect housing price by building perdictive model.

We have the some interesting features in our dataset, for instance, 


$black$

1000(Bk - 0.63)^2 where Bk is the proportion of blacks by town.

$crim$

per capita crime rate by town.

How would these enviornment variables affect a house's value?


I found this data set from our class repo, more information could be found at https://www.kaggle.com/c/boston-housing/overview/description

# Data description 

The medv variable is the target variable.

The Boston data frame has 506 rows and 14 columns.

This data frame contains the following columns:

crim
per capita crime rate by town.

zn
proportion of residential land zoned for lots over 25,000 sq.ft.

indus
proportion of non-retail business acres per town.

chas
Charles River dummy variable (= 1 if tract bounds river; 0 otherwise).

nox
nitrogen oxides concentration (parts per 10 million).

rm
average number of rooms per dwelling.

age
proportion of owner-occupied units built prior to 1940.

dis
weighted mean of distances to five Boston employment centres.

rad
index of accessibility to radial highways.

tax
full-value property-tax rate per $10,000.

ptratio
pupil-teacher ratio by town.

black
1000(Bk - 0.63)^2 where Bk is the proportion of blacks by town.

lstat
lower status of the population (percent).

medv
median value of owner-occupied homes in $1000s.

## Source
Harrison, D. and Rubinfeld, D.L. (1978) Hedonic prices and the demand for clean air. J. Environ. Economics and Management 5, 81–102.

Belsley D.A., Kuh, E. and Welsch, R.E. (1980) Regression Diagnostics. Identifying Influential Data and Sources of Collinearity. New York: Wiley.

## loading pkgs
```{r pkgs, message=FALSE}
library(tidyverse)
library(ggplot2)
library(fs)
library(purrr)
library(stringr)
library(assertr)
library(caret)
library(janitor)
```

## load data

```{r load data, message=FALSE}
df <- read_csv("./data/BostonHousing.csv")
```

## some functions
```{r functions}
#for check how many unique values for each variable.
col_uni <- function(df){
  map(
    map(df,unique), # apply the unique function to each column, return the unique value of each column.
    length) #apply the length function to the unique value of each column, return how long the unique value is for each column so that we can know how many unique values for each column.
}
```


## overview

```{r #dataoverview}
str(df)
```
## check the dataset
```{r check}
# check how many missing values in our dataset, result is 0.
sum(is.na(df))

# check the limit (based on description) for each variable 
df %>% 
  assert(in_set(c(1, 0)), chas)%>% 
  assert(in_set(c(0:24)), rad)%>% 
  assert(within_bounds(0,1), nox) %>%
  assert(within_bounds(0,100), zn)%>%
  assert(within_bounds(0,100), crim)%>%
  assert(within_bounds(0,Inf),indus)%>%
  assert(within_bounds(0,120), age) %>%
  assert(within_bounds(0,Inf), dis) %>%
  assert(within_bounds(0,100), ptratio) %>%
  assert(within_bounds(0,Inf), tax) %>%
  assert(within_bounds(0,Inf), medv) %>%
  assert(within_bounds(0,Inf), b) %>%
  assert(within_bounds(0,100), lstat)
```

## check how many unique values each variables have.

From the result below, we can find that there are some variables only have few unique values.

Combining the result below with the information from the data description,"rad" & "chas" should be factor variables.
```{r check var}
col_uni(df)
```
